On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-08 main.tex
Update main.tex
Updated algorithm, corrections

The following is our main algorithm. In step 5, we use  \cite[Algorithm 2]{SH} to solve a square system. This subroutine is randomized. In order to guarantee a higher probability of success, we repeat the calculation $k$ times. This subroutine also requires a straight-line program as input, which we compute from $f^\mA$ and its partial derivatives. 

@@

\nl Construct $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $\mA \in S^{n^2}$, and  $\bm \sigma \in T^{n-1}$\;

@@

\nl Run \cite[Algorithm 2]{SH} $k \geq \lg(3n/\epsilon)$ times with a straight-line program computed from 
$\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$\;

>>>>

The following is our main algorithm. In step 5, we use  \cite[Algorithm 2]{SH} to solve a square system, where this subroutine is randomized. In order to guarantee a higher probability of success, we repeat the calculation $k$ times. This subroutine requires the input to be in the form of a straight-line program, which we compute from $f^\mA$ and its partial derivatives. 

@@

\nl Construct $S := \{1,2,\hdots,\lceil(3\epsilon^{-1})6n^3(2d)^{2n}\}\rceil$ and $T := \{1,2,\hdots,\lceil (3\epsilon^{-1})nd^{2n}\rceil\},$ and randomly choose $\mA \in S^{n^2}$, and  $\bm \sigma \in T^{n-1}$\;

@@

\nl Prepare a straight-line program $\Gamma$ that computes the system of polynomials
$\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$ and run \cite[Algorithm 2]{SH}, with input $\Gamma,$ and with $ k \geq \lg(3n/\epsilon)$ repetitions\; 
